Constraint Programming - Inside Gecode

### 2014-05-08 paper.tex
improved part on branch-and-bound
centered figures
reduced two figures to only one

	\begin{figure}
		\begin{tikzpicture}
			\coordinate (a) at (0, 0);
			\coordinate (b) at (4, 0);
			\coordinate (c) at (5, 3);
			\coordinate (d) at (3, 6);
			\coordinate (e) at (-1, 2);
			\coordinate (f) at (2, 0);
			\coordinate (g) at (intersection of e--c and f--d);

			\draw[very thick, fill=blue, fill opacity=0.1] (a) -- (b) -- (c) -- (d) -- (e) -- (a);
			\draw[pattern=north west lines, pattern color=gray] (a) -- (b) -- (c) -- (e) -- (a);
			\draw[pattern=north east lines, pattern color=gray] (f) -- (g) -- (c) -- (b) -- (f);
		\end{tikzpicture}	
		\center
		\caption{Branch-and-reduce applied to a search space}
		\label{fig:branchAndReduce}
	\end{figure}

@@

	\begin{figure}
		\begin{tikzpicture}
			\coordinate (a) at (0, 0);
			\coordinate (b) at (4, 0);
			\coordinate (c) at (5, 3);
			\coordinate (d) at (3, 6);
			\coordinate (e) at (-1, 2);
			\coordinate (f) at (2, 0);
			\coordinate (g) at (intersection of e--c and f--d);

			\draw[very thick] (a) -- (b) -- (c) -- (d) -- (e) -- (a);
			\draw (a) -- (b) -- (c) -- (e) -- (a);
			\draw (f) -- (g) -- (c) -- (b) -- (f);
			\node at (2.5, 4) {$P_0$};
			\node at (1, 1) {$P_1$};
			\node at (3.5, 1.5) {$P_2$};
		\end{tikzpicture}	
		\center
		\caption{Possible candidates for a solution and the related search space}
		\label{fig:bounding}
	\end{figure}

	Consider for this \reffig{fig:bounding}, where already a certain optimum $f_1$ was found in subproblem $P_1$. If now the relaxed optimum $f_{P0}$ is worse than this optimum
	\begin{equation}
		f_{P0} > f_1
	\end{equation}
	the whole subproblem $P_{0}$ can be pruned and it is not necessary to enumerate the solution candidates in it (or to apply split it further up).

>>>>

	\begin{figure}
		\center
		\begin{tikzpicture}
			\coordinate (a) at (0, 0);
			\coordinate (b) at (4, 0);
			\coordinate (c) at (5, 3);
			\coordinate (d) at (3, 6);
			\coordinate (e) at (-1, 2);
			\coordinate (f) at (2, 0);
			\coordinate (g) at (intersection of e--c and f--d);

			\draw[very thick] (a) -- (b) -- (c) -- (d) -- (e) -- (a);
			\draw (a) -- (b) -- (c) -- (e) -- (a);
			\draw (f) -- (g) -- (c) -- (b) -- (f);
			\draw[fill=blue, fill opacity=0.2] (c) -- (d) -- (e) -- (c);
			\draw[fill=green, fill opacity=0.2] (a) -- (f) -- (g) -- (e) -- (a);
			\draw[fill=brown, fill opacity=0.2] (f) -- (g) -- (c) -- (b) -- (f);
			\node at (2.5, 4) {$P_0$};
			\node at (1, 1) {$P_1$};
			\node at (3.5, 1.5) {$P_2$};
		\end{tikzpicture}	
		\caption{Splitting of a search space into three subproblems and the possible candidates for solutions}
		\label{fig:branchAndBound}
	\end{figure}

@@

	Consider for this \reffig{fig:branchAndBound}, where already a certain optimum $f$ was found in subproblem $P_1$. If now the relaxed optimum $f_{P0}$ in $P_0$ and $f_{P2}$ in $P_2$ is worse than this optimum
	\begin{equation}
		f_{P0} > f
	\end{equation}
	\begin{equation}
		f_{P2} > f
	\end{equation}
	the whole subproblems $P_{0}$ and $P_{2}$ can be pruned and it is not necessary to enumerate the solution candidates in them (or to split them further up).
